Reproducible Workflow on a Public Cloud for Computational Fluid Dynamics

### 2019-08-14 tex/MesnardoBarba2019.tex
Add word "ideally" for reproducibility requirement

To study the flow around the flying snake, we developed a CFD software called PetIBM\cite{chuang_et_al_2018}, an open-source toolbox that solves the two- and three-dimensional incompressible Navier-Stokes equations using a projection method (seen as an approximate block-LU decomposition of the fully discretized equations\cite{perot_1993}) and an immersed-boundary method (IBM).
Within this framework, the fluid equations are solved over an extended grid that does not conform to the surface of the immersed body.
To model the presence of the body, the momentum equation is augmented with a forcing term that is activated in the vicinity of the immersed boundary.
This technique allows the use of simple fixed structured Cartesian grids to solve the equations.
PetIBM implements immersed boundary methods (IBMs) that fit into the projection method; in the present study, we use the IBM scheme proposed in \cite{li_et_al_2016}.
PetIBM runs on distributed-memory architectures using the efficient data structures and parallel routines from the PETSc library.
The software also implements the possibility to solve linear systems on multiple GPU devices distributed across the nodes with the NVIDIA AmgX library and our AmgXWrapper\cite{chuang_barba_2017}.
One of the requirements for reproducible computational results is to make the code available under a public license (allowing reuse and modification by others).
In that regard, PetIBM is open source, version-controlled on GitHub,\footnote{PetIBM (version 0.4): \url{https://github.com/barbagroup/PetIBM}} and shared under the permissive (non copy-left) BSD-3 clause license.
We also provide a Docker image of PetIBM on DockerHub and its Dockerfile is available in the GitHub repository of the software.

>>>>

To study the flow around the flying snake, we developed a CFD software called PetIBM\cite{chuang_et_al_2018}, an open-source toolbox that solves the two- and three-dimensional incompressible Navier-Stokes equations using a projection method (seen as an approximate block-LU decomposition of the fully discretized equations\cite{perot_1993}) and an immersed-boundary method (IBM).
Within this framework, the fluid equations are solved over an extended grid that does not conform to the surface of the immersed body.
To model the presence of the body, the momentum equation is augmented with a forcing term that is activated in the vicinity of the immersed boundary.
This technique allows the use of simple fixed structured Cartesian grids to solve the equations.
PetIBM implements immersed boundary methods (IBMs) that fit into the projection method; in the present study, we use the IBM scheme proposed in \cite{li_et_al_2016}.
PetIBM runs on distributed-memory architectures using the efficient data structures and parallel routines from the PETSc library.
The software also implements the possibility to solve linear systems on multiple GPU devices distributed across the nodes with the NVIDIA AmgX library and our AmgXWrapper\cite{chuang_barba_2017}.
One of the requirements for reproducible computational results is to make the code available under a public license (ideally allowing reuse and modification by others).
In that regard, PetIBM is open source, version-controlled on GitHub,\footnote{PetIBM (version 0.4): \url{https://github.com/barbagroup/PetIBM}} and shared under the permissive (non copy-left) BSD-3 clause license.
We also provide a Docker image of PetIBM on DockerHub and its Dockerfile is available in the GitHub repository of the software.
